### 2022-03-16 tikz/xlrm.tex
edits esp base SLR priors on NOAA report

    \node [font=\color{rosso}\selectfont] at (-4.5, 3.5) {\Large Uncertainties};
    \node [relation] (relationships) at (0, -0.5) {Engineering and economic models};
    \node [uncertainty] (surge) at (-3.25, 2.5) {Storm surge\\{\footnotesize (draws from 1 posterior)}};
    \path [line] (surge) to (relationships);

    \node [font=\color{thirds}\selectfont] at (0, -1.75) {\Large Relationships};
    \node [uncertainty] (slr) at (-3.5, -1) {Sea level\\{\footnotesize (16 PDFs)}};
    \path [line] (slr) to (relationships);

    \node [font=\color{giallo}\selectfont] at (0, 3) {\Large Levers};
    \node [lever] (elevate) at (0, 2) {How high to elevate?};
    \path [line] (elevate) to (relationships);

    \node [font=\color{giallo}\selectfont] at (3.5, 2.25) {\Large Metrics};
    \node [metric] (ccost) at (3.5, 1) {Up-front\\(construction)\\cost};
    \path [line] (relationships) to (ccost);
    \node [metric] (fcost) at (3.5, -1) {Lifetime expected damages};
    \path [line] (relationships) to (fcost);

    \node[uncertainty] (rcp) at (-4.5, -2.5) {RCP scenario\\{\footnotesize (4 Scenarios)}};
    \node[uncertainty] (ice) at (-4.5, 0.75) {Ice sheet dynamics\\{\footnotesize (4 Models)}};
    \path [line] (rcp) to (slr);
    \path [line] (ice) to (slr);

>>>>

    \node [font=\color{rosso}\selectfont] at (-6, 2.5) {\Large Uncertainties};
    \node [relation] (relationships) at (0, -0.5) {Engineering and economic models};
    \node [uncertainty] (surge) at (-3, 1.5) {Storm surge};
    \path [line] (surge) to (relationships);

    \node [font=\color{thirds}\selectfont] at (0, -2) {\Large Relationships};
    \node [uncertainty] (slr) at (-3.5, -0.5) {Sea level};
    \path [line] (slr) to (relationships);

    \node [font=\color{giallo}\selectfont] at (0, 2.5) {\Large Levers};
    \node [lever] (elevate) at (0, 1.5) {How high to elevate?};
    \path [line] (elevate) to (relationships);

    \node [font=\color{giallo}\selectfont] at (3.5, 2.5) {\Large Metrics};
    \node [metric] (ccost) at (3.5, 1) {Up-front\\(construction)\\cost};
    \path [line] (relationships) to (ccost);
    \node [metric] (fcost) at (3.5, -1) {Lifetime expected damages};
    \path [line] (relationships) to (fcost);

    \node[uncertainty] (rcp) at (-6, -1.5) {RCP scenario\\{\footnotesize (4 Scenarios)}};
    \node[uncertainty] (ice) at (-6, 0.75) {Ice sheet dynamics\\{\footnotesize (4 Models)}};
    \path [line] (rcp) to (slr);
    \path [line] (ice) to (slr);
